Scenario 2 - MPX in the EU

### 2022-11-06 MS3.Rmd
working on data dictionary

```{r packages}
library(ggplot2)
library(tidyverse)
library(readr)
library(lubridate)
library(stringr)
library(readxl)
```
```{r}
euro_mpx_cases <- read_csv("files/euro_mpx_cases.csv")
euro_census_stats <- read_csv("files/euro_census_stats.csv")
euro_pop_denominators <- read_csv("files/euro_pop_denominators.csv")
world_country_regions <- read_csv("files/phw251_projectdata-d6f7578ccda8b47b98f4ab30005bbd76acf496ec/world_country_regions.csv")
```
\newpage

@@

```{r}
#Upload the Data Dictionary for the central data-frame: "euro_mpx_cases"
Data_Dictionary <- read_excel("~/PHW251_Fall2022/251/MS3_data_dictionary.xlsx")
Data_Dictionary

>>>>

```{r packages}
library(ggplot2)
library(tidyverse)
library(readr)
library(lubridate)
library(stringr)
library(readxl)
```
```{r}
euro_mpx_cases <- read_csv("files/euro_mpx_cases.csv")
euro_census_stats <- read_csv("files/euro_census_stats.csv")
euro_pop_denominators <- read_csv("files/euro_pop_denominators.csv")
world_country_regions <- read_csv("files/world_country_regions.csv")
```
\newpage

@@

```{r}
#Upload the Data Dictionary for the central data-frame: "euro_mpx_cases"
#Data_Dictionary <- read_excel("~/PHW251_Fall2022/251/MS3_data_dictionary.xlsx")
#Data_Dictionary

Floor month
year-MM-DD

EU region (European Region)
Western Europe
Eastern Europe
Western Europe
Northern Europe
Souther Europe

Country Code (2 Letter Alpha Country Code)
AT Austria
BE Belgium
BG Bulgaria
CY Cyprus
CZ Czechia
DE Germany
DK Denmark
EE Estonia
EL Greece
ES Spain
FI Finland
FR France
HR Croatia
HU Hungary
IE Ireland
IS Iceland
IT Italy
LT Lithuania
LU Luxembourg
LV Latvia
MT Malta
NL Netherlands
NO Norway
PL Poland
PT Portugal
RO Romania
SE Sweden
SI Slovenia
SK Slovakia

total_pop_2022

cases_grouped monthly (Monkeypox cases per month in each country)

0-1000

1000-9999

10000-99999

100000-199999

200000-499999

500000-999999

GE1000000
